### 2020-07-17 latex/sections/managerial.tex

%% The list of abbreviations is an example of a special list
%% Other lists may be added, such as lists of algorithms, symbols, theorems, etc.
%% IN CS PhD, this is sometimes centered.
\coverchapter{List of Abbreviations}%%RUM: Not mentioned
\begin{tabular}{ll}
MSc &Masters of Science\\
ML & Machine Learning\\
AI & Artificial Intelligence\\
\end{tabular}

>>>>

%% The list of abbreviations is an example of a special list
%% Other lists may be added, such as lists of algorithms, symbols, theorems, etc.
%% IN CS PhD, this is sometimes centered.
\coverchapter{List of Abbreviations}%%RUM: Not mentioned
\begin{tabular}{ll}
MSc &Masters of Science\\
ML & Machine Learning\\
AI & Artificial Intelligence\\
ANN & Artificial Neural Network\\
DNN & Deep Neural Network\\
MCTS & Monte-Carlo Tree Search\\
CAV & Concept Activation Vector\\

\end{tabular}
